---
title: "Models: Fitting and Evaluation"
execute:
  echo: false
  warning: false
  message: false
format:
  pdf:
    toc: true
    fig-height: 6
    fig-width: 8
---

```{r setup}
#| warning: FALSE
#| message: FALSE
library(coin)
library(DHARMa)
library(glmmTMB)
library(here)
library(tidyverse)
```

```{r}
mp <- readRDS(file = here::here("out", "microplastics.rds"))
pfas <- readRDS(file = here::here("out", "pfas.rds"))
```

# Microplastics

```{r}
# total microplastics, summed across all polymers
mp.total <- mp %>%
  group_by(id, category, bottle_material, source_type, adv_filtration) %>%
  summarise(particles = sum(particles)) %>%
  mutate(nd = ifelse(particles == 0, 1, 0),
         detect = ifelse(particles > 0, 1, 0))
# bottled samples only
mp.bottled <- mp %>%
  filter(category == "Bottled") %>%
  mutate(bottle_material = fct_drop(bottle_material))
# PE polymer only
mp.bottled.pe <- mp.bottled %>%
  filter(polymer == "PE")
# PET polymer only
mp.bottled.pet <- mp.bottled %>%
  filter(polymer == "PET") 
# bottled samples, total MP
mp.bottled.total <- mp.total %>%
  filter(category == "Bottled") %>%
  mutate(bottle_material = fct_drop(bottle_material))
```

## Total model

```{r}
# make municipal the reference category
mp.total <- mp.total %>%
  mutate(category = fct_relevel(category, "Municipal", "Bottled"))

model.mp.total <- glmmTMB(
  particles ~ category + bottle_material + source_type + adv_filtration,
  data = mp.total,
  family = nbinom2(),
  ziformula = ~ .,
  na.action = na.omit
)
summary(model.mp.total)
saveRDS(model.mp.total, file = here::here("out", "model_mp_total.RDS"))
```

### Model evaluation

```{r}
sim.mp.total <- DHARMa::simulateResiduals(model.mp.total)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotQQunif(sim.mp.total)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotResiduals(sim.mp.total)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotResiduals(sim.mp.total, form = mp.total$category)
```

## Bottled model

```{r}
mp.bottled.total <- mp.bottled.total %>%
  mutate(bottle_material = fct_relevel(bottle_material, "PET", "HDPE"))

model.mp.bottled.total <- glmmTMB(
  particles ~ bottle_material + source_type + adv_filtration,
  data = mp.bottled.total,
  family = nbinom2(),
  ziformula = ~ .,
  na.action = na.omit
)
summary(model.mp.bottled.total)
saveRDS(model.mp.bottled.total, file = here::here("out", "model_mp_bottled_total.RDS"))
```

The large standard errors in the zero-inflated component are because source_type and adv_filtration are very collinear.

```{r}
table(mp.bottled.total$source_type, mp.bottled.total$adv_filtration)
```

```{r}
table(mp.bottled.total$source_type, mp.bottled.total$particles > 100)
```

```{r}
table(mp.bottled.total$adv_filtration, mp.bottled.total$particles > 100)
```

```{r}
mp.bottled.total %>%
  filter(particles > 100 & adv_filtration == "Yes")
```

So, we do not look at the zero-inflated portion of the model, as the estimates and inference are not reliable.

We check that neither variable is significant on its own:

```{r}
model.mp.bottled.total1 <- glmmTMB(
  particles ~ bottle_material + source_type,
  data = mp.bottled.total,
  family = nbinom2(),
  ziformula = ~ .,
  na.action = na.omit
)
summary(model.mp.bottled.total1)
```

```{r}
model.mp.bottled.total2 <- glmmTMB(
  particles ~ bottle_material + adv_filtration,
  data = mp.bottled.total,
  family = nbinom2(),
  ziformula = ~ .,
  na.action = na.omit
)
summary(model.mp.bottled.total2)
```

Because neither variable is significant in the zero-inflated component on its own, we are reasonably confident there is no difference in detection probability by either source type or advanced filtration. To report p-values, we instead report the Fisher exact test p-values, which don't control for other variables, as the p-values from the zero-inflated portion of the model are not reliable. See below for the Fisher exact tests.

### Model evaluation

```{r}
sim.mp.bottled <- DHARMa::simulateResiduals(model.mp.bottled.total)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotQQunif(sim.mp.bottled)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotResiduals(sim.mp.bottled)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotResiduals(sim.mp.bottled, form = mp.bottled.total$source_type)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotResiduals(sim.mp.bottled, form = mp.bottled.total$adv_filtration)
```

### Fisher exact tests

#### Probability of detection: source

```{r}
mean(mp.bottled.total %>% filter(source_type == "Spring") %>% pull(detect))
mean(mp.bottled.total %>% filter(source_type == "Non-spring") %>% pull(detect))
```

```{r}
table(mp.bottled.total$source_type, mp.bottled.total$detect)
```

```{r}
coin::oneway_test(detect ~ factor(source_type), 
                  data = mp.bottled.total, 
                  distribution = "exact")
```

#### Probability of detection: bottle material

```{r}
table(mp.bottled.total$bottle_material, mp.bottled.total$detect)
```

```{r}
coin::oneway_test(detect ~ factor(bottle_material), 
                  data = mp.bottled.total, 
                  distribution = "exact")
```

#### Probability of detection: advanced filtration

```{r}
mean(mp.bottled.total %>% filter(adv_filtration == "Yes") %>% pull(detect))
mean(mp.bottled.total %>% filter(adv_filtration == "No") %>% pull(detect))
```

```{r}
table(mp.bottled.total$adv_filtration, mp.bottled.total$source_type)
```

```{r}
table(mp.bottled.total$adv_filtration, mp.bottled.total$detect)
```

```{r}
coin::oneway_test(detect ~ factor(adv_filtration), 
                  data = mp.bottled.total, 
                  distribution = "exact")
```


## PE model

```{r}
mp.bottled.pe <- mp.bottled.pe %>%
  mutate(bottle_material = fct_relevel(bottle_material, "HDPE", "PET"))

model.mp.bottled.pe <- glmmTMB(
  particles ~ bottle_material + source_type + adv_filtration, 
  data = mp.bottled.pe,
  family = nbinom2(),
  ziformula = ~ .,
  na.action = na.omit
)
summary(model.mp.bottled.pe)
saveRDS(model.mp.bottled.pe, file = here::here("out", "model_mp_bottled_pe.RDS"))
```

### Model evaluation

```{r}
sim.mp.pe <- DHARMa::simulateResiduals(model.mp.bottled.pe)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotQQunif(sim.mp.pe)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotResiduals(sim.mp.pe)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotResiduals(sim.mp.pe, form = mp.bottled.pe$source_type)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotResiduals(sim.mp.pe, form = mp.bottled.pe$bottle_material)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotResiduals(sim.mp.pe, form = mp.bottled.pe$adv_filtration)
```

## PET model

```{r}
mp.bottled.pet <- mp.bottled.pet %>%
  mutate(bottle_material = fct_relevel(bottle_material, "HDPE", "PET"))

model.mp.bottled.pet <- glmmTMB(
  particles ~ source_type + bottle_material + adv_filtration, 
  data = mp.bottled.pet,
  family = nbinom2(),
  ziformula = ~ .,
  na.action = na.omit
)
summary(model.mp.bottled.pet)
saveRDS(model.mp.bottled.pet, file = here::here("out", "model_mp_bottled_pet.RDS"))
```


### Model evaluation

```{r}
sim.mp.pet <- DHARMa::simulateResiduals(model.mp.bottled.pet)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotQQunif(sim.mp.pet)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotResiduals(sim.mp.pet)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotResiduals(sim.mp.pet, form = mp.bottled.pet$bottle_material)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotResiduals(sim.mp.pet, form = mp.bottled.pet$source_type)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotResiduals(sim.mp.pet, form = mp.bottled.pet$adv_filtration)
```

# PFAS

```{r}
pfas <- pfas %>%
  mutate(concentration = replace_na(concentration, 0))
pfas.total <- pfas %>%
  group_by(id, category, source_type, adv_filtration) %>%
  summarise(concentration = sum(concentration)) %>%
  mutate(nd = ifelse(concentration == 0, 1, 0),
         detect = ifelse(concentration > 0, 1, 0))
pfas.tfa <- pfas %>%
  filter(analyte == "Trifluoroacetic acid")
pfas.rest <- pfas %>%
  filter(analyte != "Trifluoroacetic acid")
pfas.bottled <- pfas %>%
  filter(category == "Bottled")
pfas.bottled.total <- pfas.total %>%
  filter(category == "Bottled")
```

## Category and filtration

```{r}
model.pfas.total <- glmmTMB(
  concentration ~ category + adv_filtration, 
  data = pfas.total,
  family = ziGamma(link = "log"),
  ziformula = ~ .,
  na.action = na.omit
)
summary(model.pfas.total)
saveRDS(model.pfas.total, file = here::here("out", "model_pfas_total.RDS"))
```

### Model evaluation

```{r}
sim.pfas.total <- DHARMa::simulateResiduals(model.pfas.total)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotQQunif(sim.pfas.total)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotResiduals(sim.pfas.total)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotResiduals(sim.pfas.total, form = pfas.total$category)
```

```{r}
#| fig.height: 5
#| fig.width: 6
plotResiduals(sim.pfas.total, form = pfas.total$adv_filtration)
```

## Probability of detection: source

```{r}
pfas.source.prop <- pfas.bottled.total %>%
  group_by(source_type) %>%
  summarise(num.detect = sum(concentration > 0),
            num.zero = sum(concentration == 0),
            total = n()) %>%
  mutate(percent = 100 * num.detect/total)
print(pfas.source.prop)
```

```{r}
coin::oneway_test(detect ~ factor(source_type), 
                  data = pfas.bottled.total, 
                  distribution = "exact")
```

#### Probability of detection: advanced filtration

```{r}
pfas.advfilt.prop <- pfas.bottled.total %>%
  group_by(adv_filtration) %>%
  summarise(num.detect = sum(concentration > 0),
            num.zero = sum(concentration == 0),
            total = n()) %>%
  mutate(percent = 100 * num.detect/total)
print(pfas.advfilt.prop)
```

```{r}
table(pfas.bottled.total$adv_filtration, pfas.bottled.total$source_type)
```

```{r}
coin::oneway_test(detect ~ factor(adv_filtration), 
                  data = pfas.total, 
                  distribution = "exact")
```



```{r}
model.pfas.bottled.total <- glmmTMB(
  concentration ~ adv_filtration, 
  data = pfas.bottled.total,
  family = ziGamma(link = "log"),
  ziformula = ~ .,
  na.action = na.omit
)
summary(model.pfas.bottled.total)
#saveRDS(model.pfas.total, file = here::here("out", "model_pfas_total.RDS"))
```

```{r}
table(pfas.bottled.total$adv_filtration, pfas.bottled.total$source_type)
```
