---
title: "PFAS results"
execute:
  echo: false
  warning: false
  message: false
format:
  pdf:
    toc: true
    fig-height: 6
    fig-width: 8
---

```{r setup}
#| warning: FALSE
#| message: FALSE
library(glmmTMB)
library(here)
library(tidyverse)
```

```{r}
pfas <- readRDS(file = here::here("out", "pfas.rds"))
```

```{r}
# calculate the relative risk based on the OR and p0,
# the probability of success for baseline category
calc.rr <- function(or, p0)
{
  rr <- or / ( (1 - p0) + p0 * or)
  return(round(rr, 2))
}
```

# PFAS

```{r}
# various transforms of the data
pfas <- pfas %>%
  mutate(concentration = replace_na(concentration, 0))
pfas.total <- pfas %>%
  group_by(id, category, source_type, adv_filtration) %>%
  summarise(concentration = sum(concentration)) %>%
  mutate(nd = ifelse(concentration == 0, 1, 0))
pfas.tfa <- pfas %>%
  filter(analyte == "Trifluoroacetic acid")
pfas.rest <- pfas %>%
  filter(analyte != "Trifluoroacetic acid")
pfas.bottled <- pfas %>%
  filter(category == "Bottled")
pfas.bottled.total <- pfas.total %>%
  filter(category == "Bottled")
```

## Category and filtration

```{r}
model.pfas.total <- readRDS(file = here::here("out", "model_pfas_total.RDS"))
summary(model.pfas.total)
```

### Confidence intervals

**Gamma components**

```{r}
conf.pfas.total.ga <- confint(model.pfas.total)[1:3,]
conf.pfas.total.ga <- exp(conf.pfas.total.ga)
print(round(conf.pfas.total.ga, 2))
```

**Zero-inflated components**

```{r}
conf.pfas.total.zeroinf <- confint(model.pfas.total)[4:6,]
conf.pfas.total.zeroinf <- 1/exp(conf.pfas.total.zeroinf)
print(round(conf.pfas.total.zeroinf, 2))
```

## Detection in spring sources

```{r}
pfas.bottled.total.prop <- pfas.bottled.total %>%
  group_by(source_type) %>%
  summarise(num.detect = sum(concentration > 0),
            num.zero = sum(concentration == 0),
            total = n()) %>%
  mutate(percent = 100 * num.detect/total)
print(pfas.bottled.total.prop)
```


```{r}
coin::oneway_test(nd ~ factor(source_type), 
                  data = pfas.bottled.total, 
                  distribution = "exact")
```


## Conclusions

```{r}
#| echo: TRUE
pvals.pfas <- NULL
# Conclusion 1
# category, zero inflated component
pvals.pfas[1] <- 0.0278
# category, conditional component
pvals.pfas[2] <- 0.000835
# Conclusion 2
# source, fisher pitman
pvals.pfas[3] <- 1.978e-07
# Conclusion 3
# advanced filtration, zero inflated component
pvals.pfas[4] <- 0.0078
# advanced filtration, conditional component
pvals.pfas[5] <- 0.178101
names(pvals.pfas) <- c(
  "Conclusion.pfas1.1", "Conclusion.pfas1.2", 
  "Conclusion.pfas2",
  "Conclusion.pfas3.1", "Conclusion.pfas3.2"
)
```

```{r}
pvals.pfas.adj <- p.adjust(pvals.pfas, method = "BH")
```

```{r}
print(round(pvals.pfas.adj, 2))
```

# PFAS Writeup

#### Conclusion 1: Bottled v. municipal

```{r}
pfas.total.bottled <- pfas.total %>%
  filter(category == "Bottled")

p0 <- mean(pfas.total.bottled$concentration > 0)
```

```{r}
# Conclusion 1
# bottled/municipal
detect.or.est <- round(
  conf.pfas.total.zeroinf["zi.categoryMunicipal","Estimate"], 2)
detect.or.low <- round(
  conf.pfas.total.zeroinf["zi.categoryMunicipal","97.5 %"], 2)
detect.or.upp <- round(
  conf.pfas.total.zeroinf["zi.categoryMunicipal","2.5 %"], 2)
detect.rr.est <- round(
  calc.rr(conf.pfas.total.zeroinf["zi.categoryMunicipal","Estimate"], p0), 2)
detect.rr.low <- round(
  calc.rr(conf.pfas.total.zeroinf["zi.categoryMunicipal","97.5 %"], p0), 2)
detect.rr.upp <- round(
  calc.rr(conf.pfas.total.zeroinf["zi.categoryMunicipal","2.5 %"], p0), 2)
mean.est <- round(
  conf.pfas.total.ga["cond.categoryMunicipal","Estimate"], 2)
mean.low <- round(
  conf.pfas.total.ga["cond.categoryMunicipal","2.5 %"], 2)
mean.upp <- round(
  conf.pfas.total.ga["cond.categoryMunicipal","97.5 %"], 2)
```

**Conclusion 1**: 

- The odds of any PFAS being detected in a municipal water sample is `r detect.or.est` times higher compared to bottled water (adjusted ratio: `r detect.or.est`, 95% interval: [`r detect.or.low`, `r detect.or.upp`]), keeping advanced filtration fixed. This confidence interval is quite wide.
  - Unadjusted p-value: 0.0278
  - Adjusted p-value: `r round(pvals.pfas.adj["Conclusion.pfas1.1"], 2)`
- With `r round(100 * p0)`% of bottled samples having PFAS detected, the probability of detection for municipal water is  `r detect.rr.est` higher than in bottled water (adjusted ratio: `r detect.rr.est`, 95% interval for relative risk: [`r detect.rr.low`, `r detect.rr.upp`]).
  - Unadjusted p-value: 0.0278
  - Adjusted p-value: `r round(pvals.pfas.adj["Conclusion.pfas1.1"], 2)`
- For samples with PFAS detected, the mean PFAS concentration in a municipal water sample is `r mean.est`  times higher compared to bottled water (adjusted ratio: `r mean.est`, 95% interval: [`r mean.low`, `r mean.upp`])).
  - Unadjusted p-value: 0.000835
  - Adjusted p-value: `r round(pvals.pfas.adj["Conclusion.pfas1.2"], 2)`
- Overall, the evidence suggests municipal water has more PFAS compared to bottled water.

#### Conclusion 2: Spring v. non-spring

**Conclusion 2**: 

- We want to compare spring and non-spring sources. However, this is a challenging task. There are no municipal sources from spring water. Thus, if I tell you a sample is spring water, you know it is definitely bottled water. This makes it hard to disentangle the effect of the source from whether a sample is from bottled or municipal water. Thus, I want to restrict to looking at spring v. non-spring source for bottled water only. However, this still remains challenging--among non-spring bottled water, all of them have no PFAS detected! So, I should not be looking at mean concentration comparing spring and non-spring sources, because so many samples have 0 concentration. Thus, we only compare whether the proportion of samples with PFAS detected is different among spring and non-spring sources among bottled water.
- Among bottled water samples, the proportion of samples with PFAS detected is significantly higher in spring sources (85%, 23/27) compared to non-spring sources (0%, 0/13).
  - Unadjusted p-value: 1.978e-07
  - Adjusted p-value: `r round(pvals.pfas.adj["Conclusion.pfas2"], 2)`
- There is strong evidence that in bottled water, spring sources are more likely to have PFAS detected.

#### Conclusion 3, advanced filtration

```{r}
pfas.total.no <- pfas.total %>%
  filter(adv_filtration == "No")

p0 <- mean(pfas.total.no$concentration > 0)
```

```{r}
# Conclusion 1
# bottled/municipal
detect.or.est <- round(
  conf.pfas.total.zeroinf["zi.adv_filtrationYes","Estimate"], 2)
detect.or.low <- round(
  conf.pfas.total.zeroinf["zi.adv_filtrationYes","97.5 %"], 2)
detect.or.upp <- round(
  conf.pfas.total.zeroinf["zi.adv_filtrationYes","2.5 %"], 2)
detect.rr.est <- round(
  calc.rr(conf.pfas.total.zeroinf["zi.adv_filtrationYes","Estimate"], p0), 2)
detect.rr.low <- round(
  calc.rr(conf.pfas.total.zeroinf["zi.adv_filtrationYes","97.5 %"], p0), 2)
detect.rr.upp <- round(
  calc.rr(conf.pfas.total.zeroinf["zi.adv_filtrationYes","2.5 %"], p0), 2)
mean.est <- round(
  conf.pfas.total.ga["cond.adv_filtrationYes","Estimate"], 2)
mean.low <- round(
  conf.pfas.total.ga["cond.adv_filtrationYes","2.5 %"], 2)
mean.upp <- round(
  conf.pfas.total.ga["cond.adv_filtrationYes","97.5 %"], 2)
```

**Conclusion 3**: 

- Among all samples, the odds of any PFAS being detected in a sample with advanced filtration is `r 100 * (1 - detect.or.est)`%  lower compared to a sample without, keeping category fixed (adjusted ratio: `r detect.or.est`, 95% interval for odds ratio: [`r detect.or.low`, `r detect.or.upp`]).
  - Unadjusted p-value: 0.0078
  - Adjusted p-value: `r round(pvals.pfas.adj["Conclusion.pfas3.1"], 2)`
- With `r round(100 * p0)`% of samples without advanced filtration having microplastics detected, the probability of detection for samples with advanced filtration is `r 100 * (1 - detect.rr.est)`% lower than in samples without (adjusted ratio: `r detect.rr.est`, 95% interval for relative risk: [`r detect.rr.low`, `r detect.rr.upp`]).
  - Unadjusted p-value: 0.0078
  - Adjusted p-value: `r round(pvals.pfas.adj["Conclusion.pfas3.1"], 2)`
- For samples with PFAS detected, the mean PFAS concentration in a sample with advanced filtration is `r mean.est` times higher compared to a sample without, but the difference is not significant (adjusted ratio: `r mean.est`, 95% interval for multiplicative effect: [`r mean.low`, `r mean.upp`]).
  - Unadjusted p-value: 0.178101
  - Adjusted p-value: `r round(pvals.pfas.adj["Conclusion.pfas3.2"], 2)`
- Overall, the evidence suggests there is little or no difference between having advanced filtration or not.


